---
title: "PraxisColour Readme"
date: "19/02/2020"
author: "Maris Vainre"
output: github_document
---

``````{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# About PraxisColour

This is a R package to employ the unofficial [Praxis Centre for Policy Studies](http://www.praxis.ee/en/) colour palette. The package was created based on [Alex Quent's MRColour](https://github.com/JAQuent/MRColour) and [Drsimonj's blog post](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2).

# The colour palettes

```{r palettesMain, message=FALSE, warning=FALSE, include=TRUE}
library(ggplot2)
library(hrbrthemes)
library(PraxisColour)

praxis_pal("main")(3)
praxis_pal("main")(10)
```

```{r paletteBinary}
praxis_pal("binary")(2)
```
```{r paletteCool}
praxis_pal("cool")(3)
```

```{r paletteTraffic}
praxis_pal("traffic")(3)
```

```{r paletteFull}
praxis_pal("full")(7)
```

## Ggplot examples

```{r dots, warning=FALSE}
ggplot(mtcars, aes(hp, mpg)) +
    geom_point(color = praxis_cols("blue"),
               size = 8, alpha = .8) +
    theme_ipsum_tw(grid=FALSE)
```

```{r dots2, warning=FALSE}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_praxis()  +
    theme_ipsum_tw(grid=FALSE)
```
``` {r bargradient, warning=FALSE}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  scale_fill_praxis(palette = "traffic", guide = "none") +
  theme_ipsum_tw(grid=FALSE, axis_text_size = 6)
```

# Installing the package

Start by installing the devtool's package

```{r devtoolsInstall, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
install.packages("devtools")
```

Then download this package from github
```{r GithubDL, message=FALSE, warning=FALSE}
library(devtools)
install_github("mvainre/PraxisColour")
```
Now you're ready to use it:
```{r Run, message=FALSE, warning=FALSE, include=TRUE}
library(PraxisColour)
```
