---
title: "Readme"
date: "27/03/2021"
author: "Maris Vainre"
output: github_document

---

``````{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# About PraxisColour

This is a R package to employ the now almost-official [Praxis Centre for Policy Studies](http://www.praxis.ee/en/) colour palette. The package was created based on [Alex Quent's MRColour](https://github.com/JAQuent/MRColour) and [Drsimonj's blog post](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2).

# The colour palettes

```{r palettesMain, message=FALSE, warning=FALSE, include=TRUE}
library(ggplot2)
library(hrbrthemes)
library(PraxisColour)
library(tidyverse)

praxis_pal("main")(3)
praxis_pal("main")(10)
```

```{r paletteBinary}
praxis_pal("binary")(2)
```

```{r paletteBlackGold}
praxis_pal("blackgold")(2)
```


```{r paletteCool}
praxis_pal("cool")(3)
```

```{r paletteMonochrome}
praxis_pal("monochrome")(3)
```

```{r paletteFull}
praxis_pal("full")(7)
```

## Ggplot examples

```{r dotsSin, warning=FALSE}
ggplot(mtcars, aes(hp, mpg)) +
    geom_point(color = praxis_cols("blue"),
               size = 8, alpha = .8) +
    import_roboto_condensed()+
    theme_ipsum_rc(grid=FALSE)
```

```{r dots3, warning=FALSE}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_praxis()  +
    theme_ipsum_rc(grid=FALSE)
```

```{r dotsBin, warning=FALSE}

iris.sub <- iris %>%
  filter(Species != "versicolor")

ggplot(iris.sub, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_praxis(palette = "binary")  +
    theme_ipsum_rc(grid=FALSE)
```

```{r dotsMono, warning=FALSE}

iris.sub <- iris %>%
  filter(Species != "versicolor")

ggplot(iris.sub, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_praxis(palette = "monochrome")  +
    theme_ipsum_rc(grid=FALSE)
```

```{r dotsBG, warning=FALSE}

iris.sub <- iris %>%
  filter(Species != "versicolor")

ggplot(iris.sub, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_praxis(palette = "blackgold")  +
    theme_ipsum_rc(grid=FALSE)
```

```{r dots2, warning=FALSE}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_praxis(palette = "cool")  +
    theme_ipsum_rc(grid=FALSE)
```

```{r dotsall, warning=FALSE}
ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point(size = 2) +
  scale_color_praxis(palette = "full")  +
    theme_ipsum_rc(grid=FALSE)
```


``` {r barAll, warning=FALSE}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar()+
  scale_fill_praxis(palette = "full", guide = "none") +
  theme_ipsum_rc(grid=FALSE, axis_text_size = 6)
```


# Installing the package

Start by installing the devtool's package

```{r devtoolsInstall, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
install.packages("devtools")
```

Then download this package from github
```{r GithubDL, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(devtools)
install_github("mvainre/PraxisColour")
```
Now you're ready to use it:
```{r Run, message=FALSE, warning=FALSE, eval=FALSE,  include=TRUE}
library(PraxisColour)
```
